\textit{MSF: Modulated Sub-graph Finder}

### 2018-04-13 MSF_Paper_FA.tex
review to the end; but not done yet

\author[1]{Mariam R. Farman}
\author[1,2]{Fabian Amman}
\author[1]{Ivo L. Hofacker}
\affil[1]{Institute for Theoretical Chemistry,Theoretical Biochemistry Group,University of Vienna, Austria}
\affil[2]{Department of Chromosome Biology, Max F. Perutz Laboratories,University of Vienna, Austria}

@@

As input, information on functional links between genes provided by
e.g.~KEGG or Reactome and information on the differential expression status
of single genes resulting from a DGEA, are required. As a result the
analysis returns sub-graphs and their joint confidence scores, reflecting
how the perturbation is migrated through the network. Furthermore, the
entry points of perturbation in the networks and overlap with conventional
pathway categories are returned. The output is prepared for convenient
visualisation with the \TODO{StringApp, available as a Cytoscape plug-in.}

All of this can be helpful to understand the cause and effect of a stimulus
and might inform about potential points of intervention. The proposed
algorithm was implemented as a java program, which was named
\texttt{Modulated Sub-graph Finder} (abbreviated
\texttt{MSF}). \texttt{MSF} can help transform the information obtained
from DGEA into comprehensible knowledge of signal transduction of genes and
thereby being a valuable complement to existing pathway based
methods. \texttt{MSF} is freely accessible on github \TODO{which licence?}.

@@

To demonstrate its usefulness, \texttt{MSF} is applied to an RNAseq data
set of primary human monocyte-derived macrophages (MDMs) infected with
Ebola virus (GSE84188)~\cite{Olejnik}. Ebola Virus (EBOV) belongs to the
Filoviridea family; filamentous, enveloped and single stranded RNA
viruses. EBOV causes hemorrhagic fever in humans, inducing the host innate
and adaptive immune response to be unable to control virus
infection~\cite{Prins}. Until now, there are no approved antiviral drugs
for the treatment of Ebola virus infection~\cite{Konde,Rhein}.  The initial
targets of EBOV are the macrophages and dendritic immune
cells~\cite{Falasca,Rhein}. EBOV inhibits the critical innate immune
response of the host, which includes the activation of alpha/beta
interferon (IFN-$\alpha / \beta$)~\cite{Prins,Konde,Cardenas}. It has been
proposed that IFN-$\alpha / \beta$ should be tested against Ebola for its
antiviral activity through clinical trials~\cite{Konde}. \TODO{I do not get
this sentence: Since the data was most recent and the infection was
carried out in human macrophages, it helped us comprehend the innate
immune response of host}. The aim of testing this data with \texttt{MSF} was
to identify the modulated sub-graphs and check if \texttt{MSF} is able to
identify the IFN-$\alpha / \beta$ gene as one of the sources, and show that
the capability to close ``gaps'' by using information of neighboring genes
is effective.

\TODO{TODO: If MSF is not applied but only significant genes are mapped on
  the reactom data set, into how many sub-graphs would the data fall apart?
  in other words: how many genes are only significant because they are part
  of a significant sub-graph but are not on there own?}

EBOV infection count data was downloaded from GEO (GSE84188). Differential
gene expression analysis was performed on the count data with edgeR package
(version 3.4.2)~\cite{edgeR}. The DEG analysis results generated by edgeR
were used as input for \texttt{MSF}. The EBOV infection experiments
describe the course of infection at three time-points 6, 24 and 48 hour
post infection (hpi). For the earliest time point at 6~hpi, five modulated
sub-graphs were identified with 41, 107, and 18 genes. Two of the five
sub-graphs were less than 4 genes long. Most of the genes part of the
sub-graphs were cytokines, chemokines (CXCL10, CCL8) and Interleukin genes
(IL6, IL27, IL23) which serve as a subset of CD4+ T helper cells. IFNB1 and
IFNA1 were both identified as two of the possible sources. Most of the
sources identified by \texttt{MSF} were type~I interferon induced genes. At
24~hpi nine modulated sub-graphs were identified with four main sub-graphs
consisting of 38, 85, 148 and 167 genes. IFNA1 was identified as one of the
sources in the most significantly modulated sub-graph. For the last
time-point 48~hpi, eleven modulated sub-graphs were identified. Eight of
the sub-graphs were less than seven genes and main sub-graphs had 39, 71
and 210 genes. IFNB1 and IFNA1 were identified as the two sources out of
the possible sources.

@@

@@

 To assess the robustness and stability of our method, Poisson distributed
 noise was added to the read counts of the three time-points data set, used
 in the previous analysis. Then DGEA was carried out on the disturbed data
 with the same parameters as for the native data using edgeR, followed by
 analysis with \texttt{MSF}. This procedure was carried out 100 times.
 Every time the genes from the modulated sub-graphs identified from noisy
 data were compared to the genes of sub-graphs identified from the native
 data. This was also done for the DEG obtained for each run, a cutoff
 \TODO{what cutoff?} was used to compare the retrieved DEG from noisy data
 to the native data.  The robustness of \texttt{MSF} and the DEG analysis
 for the time-point 6, 24, and 48~hpi are shown in
 Fig.~\ref{fig:DEGvsMSF}. The procedure how data noise was modeled can be
 considered as rather stringent, which is already reflected limited recall
 rate in the edgeR based DGEA, between \TODO{X and Y~\%}. For
 \texttt{MSF}-analysis the observed median recall rates lay between 71~\%
 (6~hpi) and 84~\% (48~hpi).

 \TODO{This paragraph makes no sense to me:
 To test \texttt{MSF's} correctness simulation was also conducted. For each
 time-point, one \texttt{MSF} identified sub-graph was selected and using
 simulation random graph was generated with the same number of genes as the
 sub-graphs utilizing the same interaction file. The simulation identified
 sources were counted from the simulated sub-graph. The objective was to
 find less sources in the simulated sub-graphs than observed in the real
 sub-graphs identified by \texttt{MSF}. Simulation results showed a chance
 of $<$10$\%$ of the 1000 random sub-graphs generated to get more sources
 than observed.}

\TODO{bis da!!}

\subsection*{Comparison}

 A comparison to other tools was performed on the same dataset using each
 software's default parameters. We compared the gene enrichment analysis in
 \texttt{MSF} identified sub-graphs to pathway analysis by
 SPIA~\cite{Tarca} for KEGG and Reactome pathway enrichment analysis for
 Reactome.  We used Cytoscape~\cite{Cyto} plugins to identify the enriched
 patwhays, CytoKegg~\cite{Cytokegg} for KEGG and Reactome
 FI~\cite{Reactome} for Reactome for \texttt{MSF} identified sub-graphs.

@@

Likewise we compared gene enrichment results of sub-graph genes identified
by \texttt{MSF} using Reactome FI to the Reactome predefined pathway
enrichment analysis. Although \texttt{MSF} and Reactome showed good
agreement on the dis-regulated pathways e.g Signaling by Interleukins,
Interleukin-10 signaling, Cytokine Signaling in Immune system, Chemokine
receptors bind chemokines, RIG-I/MDA5 mediated induction of IFN-alpha/beta
pathways, NF-kB activation, Reactome as well could not identify Toll-like
receptor signaling. This shows that \texttt{MSF} is able to identify the
important modulated genes of the early infection stage.

@@

MSF is able to identify the connected modulated genes, showing how the
signal transmission flows between the different predefined pathways. MSF is
able to identify the important genes at the early stage of infection which
at the later stage of infection became the most modulated genes. Even with
the addition of noise MSF identifies the important modulated core set of
genes. The sources identified by MSF can assist in the discovery of new
drug targets. One limitation for MSF would be an incomplete interaction
network. For the unknown or less known genes, the interactions are still
not well known and so are usually missing in the biological network in
different databases.

@@

\textbf{MSF} is a fast and robust tool to find modulated sub-graphs
from a given network. So far, it is the only tool from existing
approaches that builds the modulated sub-graph from scratch using the
network and DEG, where the predefined pathways could be seen connected
to each other. The Robustness analysis shows that \textbf{MSF} is
fairly robust against noise and thus finds core modulated sub-graphs
even if the DGEA is not carried out vigilantly. Alongside with
\textbf{MSF}, we provide a good directed cell signaling network file,
which is a subset of interactions from Reactome Functional
interactions (FIs) Version 2016 .

@@

The Ebola infection RNAseq dataset analyzed during the current study are
available in the GEO repository (GSE84188). The cell signaling network file
used is from Reactome Functional interactions (FIs) Version 2016

\subsection*{Author contributions}
FA proposed the idea. MF implemented the method. MF designed the benchmark
data set. MF analyzed the benchmark results. MF, FA, and IH contributed to
the manuscript writing. MF produced all figures. All authors read and
approved the final manuscript.

@@

This work was funded by the FWF (“Fonds zur Forderung der
wissenschaftlichen Forschung”) within the project Internationalen
Kooperationsprojektes - Intl cooperation Project (Joint Project - Lead
Agency Verfahren) with the project number (I 1988-B22). The grant was
assigned to Ivo Hofacker

@@

We thank all our colleagues who provided insight and expertise that greatly
assisted the research and all reviewers for their constructive criticism.

@@

\begin{figure*}
	\centering
	\fbox{
		\begin{minipage}{17 cm}
		\includegraphics[width=1.0\linewidth]{AlgorithmMSF.png}
		\caption{Shows the algorithm of MSF with four steps to find the modulated sub-graphs and identify sources and sinks.}
		\label{fig:pseudocodemsf}
	\end{minipage}
}

@@

\begin{figure*}
	\centering
	\fbox{
		\begin{minipage}{17 cm}
			\includegraphics[width=1.05\linewidth]{SeperatedMergedNetwork.png}
			\caption{Shows the three modulated sub-graphs identified by
				MSF at 6 hpi, where nodes are genes and edges are the
				interactions. The node coloring is associated to KEGG
				pathways referring to the colors in the legend. The graph
				edges are from Reactome. Important genes to EBOV infection
				as from literature are enlarged in the graph. The signal
				flow corresponding to each sub-graph is depicted as simple
				flow chart against each sub-graph.\label{fig:Sub-graph6hpi}}
		\end{minipage}
	}
\end{figure*}

\begin{figure*}[p]
	\centering
	\fbox{
		\begin{minipage}{17 cm}
			\includegraphics[width=16cm]{DEGvsMSF2.png}
			\caption{Graph shows the percentage of DEG
                          analysis genes and MSF identified sub-graph
                          genes recall rates 100 times for the three
                          different time points after the addition of
                          Poisson distributed noise.\label{fig:DEGvsMSF}}
			\label{label}
		\end{minipage}
	}
\end{figure*}

>>>>

\author[1]{Mariam R. Farman}
\author[1]{Ivo L. Hofacker}
\author[1,2]{Fabian Amman}
\affil[1]{Institute for Theoretical Chemistry,Theoretical Biochemistry Group,University of Vienna, Austria}
\affil[2]{Department of Chromosome Biology, Max F. Perutz Laboratories,University of Vienna, Austria}

@@

As input, information on functional links between genes provided by
e.g.~KEGG or Reactome and information on the differential expression
status of single genes resulting from a DGEA, are required. As a
result the analysis returns sub-graphs and their joint confidence
scores, reflecting how the perturbation is migrated through the
network. Furthermore, the entry points of perturbation in the networks
and overlap with conventional pathway categories are returned. The
output is prepared in a directed adjacency file, convenient for
visualization with the StringApp~\cite{StringApp}, available as a
Cytoscape plug-in~\cite{Cyto}.

All of this can be helpful to understand the cause and effect of a
stimulus and might inform about potential points of intervention. The
proposed algorithm was implemented as a java program, which was named
\texttt{Modulated Sub-graph Finder} (abbreviated
\texttt{MSF}). \texttt{MSF} can help transform the information
obtained from DGEA into comprehensible knowledge of signal
transduction of genes andl thereby being a valuable complement to
existing pathway based methods. \texttt{MSF} is freely accessible on
github under the terms of the Creative Commons Attribution 4.0
International License.

@@

To demonstrate its usefulness, \texttt{MSF} is applied to an RNAseq
data set of primary human monocyte-derived macrophages (MDMs) infected
with Ebola virus (GSE84188)~\cite{Olejnik}. Ebola Virus (EBOV) belongs
to the Filoviridea family; filamentous, enveloped and single stranded
RNA viruses. EBOV causes hemorrhagic fever in humans, inducing the
host innate and adaptive immune response to be unable to control virus
infection~\cite{Prins}. Until now, there are no approved antiviral
drugs for the treatment of Ebola virus infection~\cite{Konde,Rhein}.
The initial targets of EBOV are the macrophages and dendritic immune
cells~\cite{Falasca,Rhein}. EBOV inhibits the critical innate immune
response of the host, which includes the activation of alpha/beta
interferon (IFN-$\alpha / \beta$)~\cite{Prins,Konde,Cardenas}. It has
been proposed that IFN-$\alpha / \beta$ should be tested against Ebola
for its antiviral activity through clinical trials~\cite{Konde}. Ebola
infection data was selected to test the approach because it has been
well recognized in the literature for the last several decades. It
would be easy to cross verify the results of \texttt{MSF} with the
vast literature present on Ebola infection.  The aim of testing this
data with \texttt{MSF} was to identify the modulated sub-graphs and
check if \texttt{MSF} is able to identify the IFN-$\alpha / \beta$
gene as one of the sources, and show that the capability to close
``gaps'' by using information of neighboring genes is effective.

EBOV infection count data was downloaded from GEO (GSE84188)
\TODO{citation needed};\TODO{What was infected?}. Differential gene
expression analysis was performed on the count data with edgeR package
(version 3.4.2)~\cite{edgeR}. The DEG analysis results generated by
edgeR were used as input for \texttt{MSF}. The EBOV infection
experiments describe the course of infection at three time-points 6,
24 and 48 hour post infection (hpi). For the earliest time point at
6~hpi, five modulated sub-graphs were identified with 41, 107, and 18
genes. Two of the five sub-graphs were less than 4 genes long. Most of
the genes part of the sub-graphs were cytokines, chemokines (CXCL10,
CCL8) and Interleukin genes (IL6, IL27, IL23) which serve as a subset
of CD4+ T helper cells. IFNB1 and IFNA1 were both identified as two of
the possible sources. Most of the sources identified by \texttt{MSF}
were type~I interferon induced genes. At 24~hpi nine modulated
sub-graphs were identified with four main sub-graphs consisting of 38,
85, 148 and 167 genes. IFNA1 was identified as one of the sources in
the most significantly modulated sub-graph. For the last time-point
48~hpi, eleven modulated sub-graphs were identified. Eight of the
sub-graphs were less than seven genes and main sub-graphs had 39, 71
and 210 genes. IFNB1 and IFNA1 were identified as the two sources out
of the possible sources. Table 1 shows if \texttt{MSF} does not
consider the complete DEG results and uses different cut offs for
significant genes from DEG results, how the signal transduction would
fall apart into meaningless small sub-graphs and single unconnected
genes.

@@

\TODO{I hoped that you would not just add the table as discussed but
  would also add some discussion in the main text explaining what the
  table~\ref{tab:rawVsHartung} illustrates!}

@@

 To assess the robustness and stability of our method, Poisson
 distributed noise was added to the read counts of the three
 time-points data set, used in the previous analysis. Then DGEA was
 carried out on the disturbed data with the same parameters as for the
 native data using edgeR, followed by analysis with \texttt{MSF}. This
 procedure was carried out 100 times.  Every time the genes from the
 modulated sub-graphs identified from noisy data were compared to the
 genes of sub-graphs identified from the native data. This was also
 done for the DEG obtained for each run, a cutoff of FDR less than
 0.05 was used to compare the retrieved DEG from noisy data to the
 native data.  The robustness of \texttt{MSF} and the DEG analysis for
 the time-point 6, 24, and 48~hpi are shown in
 Fig.~\ref{fig:DEGvsMSF}. The procedure how data noise was modeled can
 be considered as rather stringent, which is already reflected limited
 recall rate in the edgeR based DGEA, between \TODO{X and Y~\%}. For
 \texttt{MSF}-analysis the observed median recall rates lay between
 71~\% (6~hpi) and 84~\% (48~hpi).

\subsection*{Comparison to existing pathway analysis tools}

 A comparison to other tools was performed on the same dataset using
 each software's default parameters. We compared the gene enrichment
 analysis \TODO{does MSF realy do a ``gene enrichment analysis''?} in
 \texttt{MSF} identified sub-graphs to pathway analysis by
 SPIA~\cite{Tarca} for KEGG and Reactome pathway enrichment analysis
 for Reactome.  We used Cytoscape~\cite{Cyto} plugins to identify the
 enriched patwhays, CytoKegg~\cite{Cytokegg} for KEGG and Reactome
 FI~\cite{Reactome} for Reactome for \texttt{MSF} identified
 sub-graphs. \TODO{I do not get those two sentences. What do those
   tools do? How do you compare the results of those tools?}

@@

Likewise we compared gene enrichment results of sub-graph genes
identified by \texttt{MSF} using Reactome FI to the Reactome
predefined pathway enrichment analysis. Although \texttt{MSF} and
Reactome showed good agreement on the dis-regulated pathways e.g
Signaling by Interleukins, Interleukin-10 signaling, Cytokine
Signaling in Immune system, Chemokine receptors bind chemokines,
RIG-I/MDA5 mediated induction of IFN-alpha/beta pathways, NF-kB
activation, Reactome as well could not identify Toll-like receptor
signaling. This shows that \texttt{MSF} is able to identify the
important modulated genes of the early infection stage. \TODO{The
  whole paragraph is hard to read and get the essentials. I suggest
  you describe in this section what the different tools work,
  especially what are the differences between them. For the results I
  suggest a plot; maybe something in the line of upset or a venn
  diagram, if appropriate.}

@@

Classic pathway analysis tools aim to detect in lists of significantly
deregulated genes enriched associations with pathway genes categorized
by their biological function and their interactions. Thereby,
depending on the tool, the internal pathway topology is considered or
neglected alltogether. The here presented tool, \texttt{MSF}, employs
a different approach, by aiming to detect sub-graphs in whole gene
regulatory networks which are significantly deregulated in a concerted
manner. To this end, neighboring genes in the user provided network
are tested for jointly common regulation. Exploiting that each gene's
abundance, although not independent from its neighbors, is measured
repeatedly on its own, sensitivity can be increased by our applied
p-value meta-analyse, namely Hartung's method. This potentially
enables to call just not significant modulated genes based on the DGEA
to be convincingly called to be part of a deregulated gene group.
Furthermore, it allows to identify connected sub-graphs, representing
the propagation of gene regulation perturbation in the input
network. A better understanding of this propagation, especially the
critical spots such as sensors, effectors, or intermediate bottlenecks
and hubs, facilitates the projection of potential intervention points,
e.g. for drug development. Since \texttt{MSF} only uses interaction
information in gene regulation network, but not the functional
grouping of the genes into functional pathways, it is especially
adapted to discover so called cross-talk between such pathways.

@@

\texttt{MSF} is a fast, robust and easy to use tool to find
concertedly modulated sub-graphs in a given network. Its
implementation in java enables it use across many operating
systems. It requires as input the results from a differential gene
expression analysis in the appropriate file format. So far the raw
output from edgeR and DESeq2~\cite{love2014moderated} are supported
\TODO{did you already implement a input option for
  DESeq2?}. Furthermore, a gene network has to be provided \TODO{do
  you check at some point if the IDs between the DGEA input and the
  gene network fit?} in the format of a simple adjacency list \TODO{is
  this true?}. For convenience \texttt{MSF} is distributed with a
prefiltered version of all directed cell signalling interactions from
Reactome Functional interactions (FIs) Version 2016. \TODO{citation
  needed} ;\TODO{did you check if reactome comes with the appropriate
  licence that we allowed to redistribute this file? this is very
  important otherwise we need good laywers} ;\TODO{In the case study
  section you never mention this file and especially the prefiltering
  of it? wouldn t you consider this crucial?}

@@

The Ebola infection RNAseq dataset analyzed during the current study
are available in the GEO repository (GSE84188) \TODO{citation
  needed}. The cell signaling network file used is from Reactome
Functional interactions (FIs) Version 2016 \TODO{citation needed}.

\subsection*{Data and Software Availability}

\TODO{see
  \url{https://f1000research.com/for-authors/article-guidelines/software-tool-articles}
  what has to be stated there}

\section*{Author contributions}
Conceptualization: FA, ILH; Funding Acquisition: ILH; Resources: ILH;
Software: MRF; Writing – Original Draft Preparation: MRF; Writing –
Review \& Editing: FA, ILH. All authors read and approved the final
manuscript.

@@

This work was funded by the FWF (“Fonds zur Forderung der
wissenschaftlichen Forschung”) within the project Internationalen
Kooperationsprojektes - Intl cooperation Project (Joint Project - Lead
Agency Verfahren) with the project number (I 1988-B22). The grant was
assigned to ILH. FA was funded by the Austrian Science Fund (FWF)
project SFB F43.

@@

We thank all our colleagues who provided insight and expertise that
greatly assisted the research and all reviewers for their constructive
criticism.\TODO{I'd suggest name those colleagues by name or remove
  the section.}

@@

\begin{figure*}
	\centering
	\fbox{
		\begin{minipage}{17 cm}
		\includegraphics[width=1.0\linewidth]{AlgorithmMSF.png}
		\caption{Graphical representation of the \texttt{MSF}
                  heuristical approach to detect modulated sub-graphs
                  in a global gene regulatory network without
                  exhaustively testing all connected sub-graphs.}
		\label{fig:pseudocodemsf}
	\end{minipage}
}

@@

\begin{figure*}
	\centering
	\fbox{
		\begin{minipage}{17 cm}
			\includegraphics[width=1.05\linewidth]{SeperatedMergedNetwork.png}
			\caption{Visualisation of the three modulated
                          sub-graphs identified by MSF at 6~h after
                          EBOV infection in gene detail and their
                          epitomized representation to depict the flow
                          of perturbation in the directed network. The
                          node coloring is associated to KEGG pathways
                          referring to the colors in the legend. The
                          graph edges are from Reactome. Important
                          genes to EBOV infection as from literature
                          are enlarged in the
                          graph.\label{fig:Sub-graph6hpi}}
		\end{minipage}
	}
\end{figure*}

\begin{figure*}[p]
	\centering
	\fbox{
		\begin{minipage}{17 cm}
			\includegraphics[width=16cm]{DEGvsMSF2.png}
			\caption{The percentage of DEG analysis genes
                          and MSF identified sub-graph genes recall
                          rates for the three different time points of
                          EBOV infection data for 100 simulation where
                          Poisson distributed noise was added to the
                          experimental deduced reads per gene
                          counts.\label{fig:DEGvsMSF}}
			\label{label}
		\end{minipage}
	}
\end{figure*}

\begin{table*}[]
	\centering
	\caption{Comparison of connected sub-graphs of modulated genes
          in the global network between the analysis results of
          \texttt{MSF} and mapping the raw list of differentially
          expressed genes from the standard edgeR analysis, applying
          different p-value cut-offs, onto the network. }
	\label{tab:rawVsHartung}
	\begin{tabular}{lll}
		\hline
		\multicolumn{1}{|l|}{}                            & \multicolumn{1}{c|}{\textbf{Total number of}}       & \multicolumn{1}{c|}{\textbf{Number of connected}}      \\ 
                \multicolumn{1}{|l|}{}                            & \multicolumn{1}{c|}{\textbf{genes in network}}      & \multicolumn{1}{c|}{\textbf{sub-graph in network}}     \\ \hline
		\multicolumn{1}{|l|}{\textbf{6hpi}}               & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{c|}{}                 \\ \hline
		\multicolumn{1}{|l|}{edgeR + MSF}                 & \multicolumn{1}{c|}{166}                                             & \multicolumn{1}{c|}{3}                \\ \hline
		\multicolumn{1}{|l|}{edgeR (p-value $\leq$ 0.1)}  & \multicolumn{1}{c|}{123}                                             & \multicolumn{1}{c|}{39}               \\ \hline
		\multicolumn{1}{|l|}{edgeR (p-value $\leq$ 0.05)} & \multicolumn{1}{c|}{123}                                             & \multicolumn{1}{c|}{47}               \\ \hline
		\multicolumn{1}{|l|}{edgeR (p-value $\leq$ 0.01)} & \multicolumn{1}{c|}{112}                                             & \multicolumn{1}{c|}{53}               \\ \hline
		\multicolumn{1}{|l|}{\textbf{24hpi}}              & \multicolumn{1}{c|}{}                                                & \multicolumn{1}{c|}{}                 \\ \hline
		\multicolumn{1}{|l|}{edgeR + MSF}                 & \multicolumn{1}{c|}{438}                                             & \multicolumn{1}{c|}{4}                \\ \hline
		\multicolumn{1}{|l|}{edgeR (p-value $\leq$ 0.1)}  & \multicolumn{1}{c|}{325}                                             & \multicolumn{1}{c|}{76}               \\ \hline
		\multicolumn{1}{|l|}{edgeR (p-value $\leq$ 0.05)} & \multicolumn{1}{c|}{305}                                             & \multicolumn{1}{c|}{102}              \\ \hline
		\multicolumn{1}{|l|}{edgeR (p-value $\leq$ 0.01)} & \multicolumn{1}{c|}{262}                                             & \multicolumn{1}{c|}{110}              \\ \hline
		\multicolumn{1}{|l|}{\textbf{48hpi}}              & \multicolumn{1}{c|}{}                                                & \multicolumn{1}{c|}{}                 \\ \hline
		\multicolumn{1}{|l|}{edgeR + MSF}                 & \multicolumn{1}{c|}{320}                                             & \multicolumn{1}{c|}{3}                \\ \hline
		\multicolumn{1}{|l|}{edgeR (p-value $\leq$ 0.1)}  & \multicolumn{1}{c|}{226}                                             & \multicolumn{1}{c|}{39}               \\ \hline
		\multicolumn{1}{|l|}{edgeR (p-value $\leq$ 0.05)} & \multicolumn{1}{c|}{207}                                             & \multicolumn{1}{c|}{62}               \\ \hline
		\multicolumn{1}{|l|}{edgeR (p-value $\leq$ 0.01)} & \multicolumn{1}{c|}{173}                                             & \multicolumn{1}{c|}{67}               \\ \hline
	\end{tabular}
\end{table*}
